Supplement to Automatic Matching of Bullet Lands

### 2016-01-06 imaging-supplement.Rnw
labelling of aligned signatures

@@

Figure~\ref{fig:aligned} gives an overview of all the signatures from bullet lands in the Hamby study aligned by barrel. Three to five bullets were fired from each barrel. The figure gives us both some insight into how well signatures match and how consistent individual characteristics are impregnated on bullets fired from each of the barrels. Signatures for some lands match remarkably well - such as land 5 from barrel 1, whereas all lands from barrel 5 show some variability both in the location and depths of peaks and valleys.
\begin{figure}[hbtp]
<<aligned, echo=FALSE, warning=FALSE, fig.width=12, fig.height=15, out.width='\\textwidth', cache=TRUE>>=
matches <- read.csv("csvs/matches.csv", header = FALSE)
matches$barrel <- rep(1:10, each=6)
matches$id <- 1:nrow(matches)
library(reshape2)
mm <- melt(matches, id.var=c("barrel", "id"), na.rm=TRUE)
mm <- subset(mm, value != "")
mm$value <- gsub("Br.* Bullet ", "", mm$value)
mm$prefix <- sprintf("Br%d Bullet ", mm$barrel)
unkns <- grep("[A-Z]",mm$value)
mm$prefix[unkns] <- "Ukn Bullet "
mm$path <- "~/papers/2015-imaging-paper/app/images/Hamby252_3DX3P1of2//"
mm$path[unkns] <- "~/papers/2015-imaging-paper/app/images/Hamby252_3DX3P2of2//"
mm$path <-   with(mm, paste0(path, prefix, value, ".x3p"))

@@

aligned <- crossSmooth %>% group_by(id) %>% do(
  data.frame(alignme(.))
)
aligned$land <- (aligned$id %% 6)
aligned$land[aligned$land==0] <- 6
aligned$bulletland <- aligned$bullet
aligned$bullet <- gsub("-[0-9]","",aligned$bullet)
library(RColorBrewer)
cols <- rep(brewer.pal(n=10, name="Paired"), length=35)[sample(35, 35, replace=TRUE)]
labels <- aligned %>% group_by(bulletland) %>% summarize(
  x = max(y),
  y = min(l30, na.rm=T),
  label = bullet[1],
  barrel = barrel[1],
  land = land[1]
)

qplot(x=y, y=l30, data=aligned, geom="line", group=bullet, colour=bullet) + 
  ylim(c(-7,7)) + xlab("") + ylab("Signature") + 
  facet_grid(facets=barrel~land, labeller="label_both") + theme_bw() +
  theme(plot.margin=unit(c(0,0,0,0), unit="cm"), legend.position="none") + 
  scale_colour_manual(values=cols) +
  geom_label(aes(x=x, y=y, label=label), data=labels, 
             inherit.aes = FALSE)
@
\caption{\label{fig:aligned}Overview of aligned signatures for all bullet lands for the ten barrels of the Hamby study. }
\end{figure}

\newpage
\section{Table of feature importance}\label{supp:randomforest}

>>>>

\usepackage{pdflscape}

@@

Figure~\ref{fig:aligned} gives an overview of all the signatures from bullet lands in the Hamby study aligned by barrel. Three to five bullets were fired from each barrel. The figure gives us both some insight into how well signatures match and how consistent individual characteristics are impregnated on bullets fired from each of the barrels. Signatures for some lands match remarkably well - such as land 5 from barrel 1, whereas all lands from barrel 5 show some variability both in the location and depths of peaks and valleys.

<<aligned, echo=FALSE, warning=FALSE,  cache=TRUE>>=
matches <- read.csv("csvs/matches.csv", header = FALSE)
matches$barrel <- rep(1:10, each=6)
matches$id <- 1:nrow(matches)
library(reshape2)
mm <- melt(matches, id.var=c("barrel", "id"), na.rm=TRUE)
mm <- subset(mm, value != "")
mm$value <- gsub("Br.* Bullet ", "", mm$value)
mm$prefix <- sprintf("Br%d Bullet ", mm$barrel)
unkns <- grep("[A-Z]",mm$value)
mm$prefix[unkns] <- "Ukn Bullet "
mm$path <- "~/papers/2015-imaging-paper/app/images/Hamby252_3DX3P1of2//"
mm$path[unkns] <- "~/papers/2015-imaging-paper/app/images/Hamby252_3DX3P2of2//"
mm$path <-   with(mm, paste0(path, prefix, value, ".x3p"))

@@

aligned <- crossSmooth %>% group_by(id) %>% do(
  data.frame(alignme(.))
)
aligned$land <- (aligned$id %% 6)
aligned$land[aligned$land==0] <- 6
aligned$bulletland <- aligned$bullet
aligned$bullet <- gsub("-[0-9]","",aligned$bullet)
library(RColorBrewer)
set.seed(20160106)
cols <- rep(brewer.pal(n=10, name="Paired"), length=35)[sample(35, 35, replace=TRUE)]
labels <- aligned %>% group_by(bulletland) %>% summarize(
  x = max(y),
  y = min(l30, na.rm=T),
  label = gsub(" Bullet","",bulletland[1]),
  barrel = barrel[1],
  land = land[1],
  bullet = bullet[1]
)
labels <- labels %>% group_by(barrel, land) %>% mutate(id=order(bulletland))
@

\begin{landscape}
\begin{figure}[hbtp]
<<aligned-first, dependson='aligned', echo=FALSE, warning=FALSE, fig.width=15, fig.height=10, out.width='7.5in'>>=
qplot(x=y, y=l30, data=subset(aligned, barrel <=5), 
      geom="line", group=bullet, colour=bullet) + 
  ylim(c(-7,7)) + xlab("") + ylab("") + xlim(c(0,3000)) +
  facet_grid(facets=barrel~land, labeller="label_both") + theme_bw() +
  theme(plot.margin=unit(c(0,0,-1,-1), unit="line"), legend.position="none") + 
  geom_label(aes(y=2.5*(id-3), label=label, colour=bullet), 
             x = 3000, data=subset(labels, barrel <= 5), 
             inherit.aes = FALSE, hjust="right", size=3) +
  scale_colour_manual(values=cols)
@
\caption{\label{fig:aligned}Overview of aligned signatures for all bullet lands for  barrels 1 to 5 of the Hamby study. }
\end{figure}

\begin{figure}[hbtp]
<<aligned-second, dependson='aligned', echo=FALSE, warning=FALSE, fig.width=15, fig.height=10, out.width='7.5in'>>=
qplot(x=y, y=l30, data=subset(aligned, barrel > 5), 
      geom="line", group=bullet, colour=bullet) + 
  ylim(c(-7,7)) + xlab("") + ylab("") + xlim(c(0,3000)) +
  facet_grid(facets=barrel~land, labeller="label_both") + theme_bw() +
  theme(plot.margin=unit(c(0,0,-1,-1), unit="line"), legend.position="none") + 
  geom_label(aes(y=2.5*(id-3), label=label, colour=bullet), 
             x = 3000, data=subset(labels, barrel > 5), 
             inherit.aes = FALSE, hjust="right", size=3) +
  scale_colour_manual(values=cols)
@
\caption{\label{fig:aligned-second}Overview of aligned signatures for all bullet lands for  barrels 5 to 10 of the Hamby study. }
\end{figure}
\end{landscape}
\newpage
\section{Table of feature importance}\label{supp:randomforest}
